%-------------------------
% Resume in Latex
% Author : Thomas Wang
% Github : https://github.com/1am9trash
% Based off of: https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge Thomas Wang}} \\
  Linkedin: \href{https://www.linkedin.com/in/thomaswang1024}{\underline{https://www.linkedin.com/in/thomaswang1024}} \\
  Github: \href{https://github.com/1am9trash}{\underline{https://github.com/1am9trash}} \\
  Email: \href{mailto:thomaswang1024@gmail.com}{\underline{thomaswang1024@gmail.com}} \\
  Mobile: +886-911-846-067 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Hsinchu, Taiwan}
      {Bachelor in Computer Science;  GPA: 4.10/4.3 (Overall), 4.26/4.3 (Major)}{September 2019 - January 2023}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} 
      DS and OOP, 
      Algorithm,
      Competitive Programming,
      Database,
      Operating System,
      Networking,
      Artificial Intelligence}}}
    \resumeSubheading
      {National Taiwan University}{Taipei, Taiwan}
      {Master in Computer Science}{July 2023 - Present}
    \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------Awards-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Bronze Prize of The 2020/2021 ICPC Asia Taipei-Hsinchu Site Programming Contest
}{Served as a representative of the NYCU Programming Challenging Contest Association.}
    \vspace{0.5pt}
    \resumeSubItem{Academic Achievements Award in 2019 Fall Semester}{Top 5 \% in the class.}
    \vspace{0.5pt}
    \resumeSubItem{2021 Facebook Hacker Cup}{Advanced to round 2 and won the T-shirt.}
    \vspace{0.5pt}
    \resumeSubItem{2021 Google KickStart Round G}{5th in Taiwan, 214th in all contestants.}
    \vspace{0.5pt}
    \resumeSubItem{2021 Google KickStart Round C}{10th in Taiwan, 318th in all contestants.}
  \resumeSubHeadingListEnd
\vspace{-5pt}

\section{Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading{Trading Campaign Team, Appier}{\small Linux, Flask, Kubernete, Jenkins, Helm, CI/CD, DevOps}
    {Backend Engineer Intern}{March 2022 – July 2022}
    \begin{itemize}
    	\setlength\itemsep{0.001em}
        \item Designed a full-stack platform with automated scripts that streamlined daily routines for users, including both frontend and backend components.
        \item Proficiently grasped the software development process, utilizing tools such as Git version control.
    	\item Managed and maintained a Kubernetes cluster, utilizing Docker containers and Jenkins for CI/CD.
    \end{itemize}    
    \resumeSubheading{Geocoding Team, Microsoft}{\small C\#, Python, Tensorflow, Bash}
    {Research and Development Intern}{July 2022 -  December 2022}
		\begin{itemize}
            \setlength\itemsep{0.001em}
            \item Developed a customized NLP model to correct address misspellings within Bing Maps, improving the accuracy of search results.
            \item Implemented comprehensive optimizations across the model pipeline connected to the live service, resulting in a significant reduction in latency.
		\end{itemize}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Raspberry pi OS}{(Work in progress)}
      \begin{itemize}
        \setlength\itemsep{0.001em}
		\item Implemented operating system kernels from scratch on an aarch64 board, demonstrating expertise in low-level systems programming.
        \item Developed and integrated exception handling and interrupt mechanisms from EL0 to EL3, and designed memory management modules.
        \item Validated the implementation of the operating system kernels using GDB and QEMU emulator tools to ensure robustness and functionality.
	 \end{itemize}
    \vspace{2pt}
    \resumeSubItem{Credit and grade calculation platform for NYCU student}{(Stop to maintain)}
      \begin{itemize}
        \setlength\itemsep{0.001em}
		\item Built frontend with HTML/CSS, Redux.js and used Firebase as backend for seamless data management.
	 \end{itemize}
    \vspace{2pt}
\resumeSubHeadingListEnd
\vspace{-5pt}

\section{Skills Summary}
  \resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~C, C++, Python, Verilog, SQL, Bash, Assembly}
	\resumeSubItem{Frameworks}{~~~~Flask, TensorFlow, Keras}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Kubernetes, Docker, Git, Helm, Jenkins, PostgreSQL, MySQL}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Win, Raspberry}
  \resumeSubHeadingListEnd

\end{document}
