%-------------------------
% Resume in Latex
% Author : Thomas Wang
% Github : https://github.com/1am9trash
% Based off of: https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
      \textbf{#1}: #2
  } \vspace{-2pt}
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    #1
  } \vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingOneLine}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand{\labelitemi}{\textcolor{black}{\textbullet}}
\renewcommand{\labelitemii}{\textcolor{black}{$\circ$}}

%-----------------------------

\begin{document}

% heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Thomas Wang } \\
  Linkedin: \href{https://www.linkedin.com/in/thomaswang1024}{\underline{https://www.linkedin.com/in/thomaswang1024}} \\
  Github: \href{https://github.com/1am9trash}{\underline{https://github.com/1am9trash}} \\
  Email: \href{mailto:thomaswang1024@gmail.com}{\underline{thomaswang1024@gmail.com}} \\
  Mobile: +886-911-846-067
\end{tabular*}

% education
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Hsinchu, Taiwan}
      {B.S. in Computer Science; GPA: 4.10/4.30 (Overall), 4.26/4.30 (Major)}{Sep 2019 – Jan 2023}
    \resumeItemListStart
      \resumeItem{Course}{Core Course Scholarship (Top 5\%) in \textbf{DS and OOP}, \textbf{Algorithms}, and \textbf{Computer Organization}}
      \resumeItem{TA}{University-appointed one-on-one academic tutor for student-athletes in core CS courses}
    \resumeItemListEnd
    \resumeSubheading
      {National Taiwan University}{Taipei, Taiwan}
      {M.S. in Computer Science; ECLab, Advisor: Prof. Chia-Lin Yang}{Sep 2023 - Present}
    \resumeItemListStart
      \resumeItem{Course}{\textbf{CUDA Programming}, \textbf{Compiler}, and \textbf{RTOS}}
      \resumeItem{TA}{Teaching Assistant for \textbf{Computer Architecture} in Fall 2023 and Fall 2024}
      \resumeItem{Research}{Accelerating Test-Time Compute with a Consumer-grade GPU}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5pt}

% awards
\section{Competition and Honors}
  \resumeSubHeadingListStart
    \resumeSubItem{Academic Achievement Award (Fall 2019)}{Top 5\% of class based on academic performance}
    \resumeSubItem{ICPC Asia Taipei-Hsinchu Regional Contest (2020, 2021)}{Bronze Medal; represented NYCU}
    \resumeSubItem{NCPC – National Collegiate Programming Contest (2021)}{Honorable Mention}
  \resumeSubHeadingListEnd
\vspace{-5pt}

% experiments
\section{Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Trading Campaign Team, Appier}{\small Linux, Flask, K8s, Jenkins, Helm}
      {Backend Engineer Intern}{Mar 2022 – Jun 2022}
      \resumeItemListStart
        \resumeItemWithoutTitle{Developed a full-stack automation platform to streamline internal campaign workflows, including both frontend and backend components.}
      \resumeItemWithoutTitle{Maintained Kubernetes clusters and implemented CI/CD pipelines using Docker, Jenkins, and Helm.}
      \resumeItemWithoutTitle{Collaborated with cross-functional teams and adopted Git-based workflows in an Agile environment.}
    \resumeItemListEnd
  
    \resumeSubheading
      {Geocoding Team, Microsoft}{\small Linux, C\#, Python, TensorFlow}
      {RD Intern}{Jul 2022 – Dec 2022}
      \resumeItemListStart
        \resumeItemWithoutTitle{Designed and deployed a custom NLP model to correct misspelled addresses in Bing Maps, enhancing geocoding accuracy and user search relevance.}
        \resumeItemWithoutTitle{Optimized the end-to-end model pipeline in the live service, reducing latency and improving system responsiveness.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5pt}

% projects
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheadingOneLine{Raspberry Pi OS}{\small C, Bare-metal, OS}
    \resumeItemListStart
      \resumeItemWithoutTitle{Built an operating system kernel from scratch on the aarch64 board, including linker script, bootloader, UART shell, filesystem, and exception/interrupt handling from EL0 to EL3.}
      \resumeItemWithoutTitle{Implemented a dynamic memory allocator (startup heap + buddy system).}
      \resumeItemWithoutTitle{Validated the implementation of the operating system kernels using GDB and QEMU emulator tools.}
    \resumeItemListEnd
    
    \resumeSubheadingOneLine{SDR HDR Converter}{\small Rust}
    \resumeItemListStart
      \resumeItemWithoutTitle{Developed a lightweight image converter for HDR/SDR formats.}
      \resumeItemWithoutTitle{Supported signal transforms (PQ, HLG, Gamma709), color space conversion (Rec.709, Rec.2020), and bit-depth quantization (8-bit, 16-bit).}
    \resumeItemListEnd

  \resumeSubheadingOneLine{Cuda/ROCm SGEMM Kernel}{\small cuda/ROCm, C++}
    \resumeItemListStart
      \resumeItemWithoutTitle{Implemented and progressively optimized SGEMM (single-precision matrix multiplication) kernels from scratch.}
      \resumeItemWithoutTitle{Applied optimization techniques including global memory coalescing, shared memory tiling, register blocking, and vectorized access to approach cuBLAS-level performance.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-5pt}

% skill
\section{Skills Summary}
  \resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~C, C++, Python, Rust}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, Docker, Shell Script, GDB, K8s, Helm, Jenkins, SQL}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Win, Cuda/ROCm}
  \resumeSubHeadingListEnd

\end{document}